---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ggrounded

<!-- badges: start -->

[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/botan/ggrounded/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/botan/ggrounded/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/botan/ggrounded/branch/main/graph/badge.svg)](https://app.codecov.io/gh/botan/ggrounded?branch=main)
[![CRAN status](https://www.r-pkg.org/badges/version/ggrounded)](https://CRAN.R-project.org/package=ggrounded)
<!-- badges: end -->

A mini-package for creating bar plots with rounded corners using ggplot2.

## Installation

You can install the development version of ggrounded from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("botan/ggrounded")
```

## Example

This is a very basic example:

```{r example}
library(ggrounded)
library(ggplot2)

ggplot(data.frame(x = letters[1:3], y = c(2.3, 1.9, 3.2)), aes(x, y)) +
geom_col_rounded()
```

## Code of Conduct

Please note that the ggrounded is released with a [contributor code of conduct](https://www.contributor-covenant.org/version/2/1/code_of_conduct.html). By contributing in this project you agree to abide by its terms.

## License

This package is released under the MIT License.
